% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{helvet} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
%\usepackage[margin=2.5 cm]{geometry}
\usepackage{hyperref}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\begin{document}

\name{Sean C. Perkins}
% \address used twice to have two lines of address
\address{Address: P.O. Box 154 Gaysville, VT 05746}
\address{Email: perkinsean@gmail.com Cell Phone: (802) 222-7749} 


 
\begin{resume}
 
 
\section{EDUCATION} {University of Vermont} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                {\sl {\bfseries Major:}}  B.A. Computer Science \\
                {\sl {\bfseries Minor:}} German  
                 
                
\section{LANGUAGES, \\ SKILLS} {\sl Software:} Python, Java(working knowledge), HTML5, CSS3, Javascript, Twitter Bootstrap, Git, Drupal, Jekyll, Google Analytics, SharePoint.  \\           
 {\sl Operating Systems:} Linux, Windows, Mac OS X \\
 {\sl Business Skills:} Great communication skills, works well in teams.\\
 
\section{WORK \\ EXPERIENCE}  {\sl {\bfseries Web Developer}} \hfill Spring 2014 \\
                Xenon Apps, Burlington, VT
                 \begin{itemize}  \itemsep -2pt 
                 \item Volunteered to design and develop xenonapps.com, a group of volunteer programmers.
                 \item Generated a static site with Harp.js to host fast and secure web pages featuring company projects, roster and contact form.
                 \item Used LESS CSS framework to create sleek and responsive layouts for all web pages.
                 \end{itemize} 

                {\sl {\bfseries Web Development Intern}}  \hfill September 2012 - December 2012 \\
                Brandthropology, inc.  Burlington, VT
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Helped work on company projects updating and implementing custom modules for Drupal 6 and 7, while also learning to use Git version control.
                \item Used HTML, Javascript, CSS and jQuery to create and update web pages based on composites made by the graphic designer.
	     \item Routinely updated content and installed Google Analytics to monitor website traffic for client websites as well as the company's own site.
                \end{itemize}
 
                {\sl {\bfseries IT Intern}} \hfill June 2012- August 2012 \\
                Vermont Housing Finance Agency, Burlington, VT
                 \begin{itemize}  \itemsep -2pt 
                 \item Main project focused on migrating PDFs and respective metadata out of proprietary Canon ImageWare software into a SharePoint intranet site. Implemented custom Visual Basic scripts to accomplish this, as well as powershell scripts to operate on the data in SharePoint.
                 \item Updated website content and made improvements to the website's PHP code.
                 \item Provided general assistance to employees within the agency, including hardware and software upgrades, system log checks, presentation setup, and daily server backup checks.
                 \end{itemize} 

	      {\sl {\bfseries IT Intern}} \hfill Winter Break '11-'12, '12-'13 \\
	      Connor Homes, LLC, Middlebury, VT
	     \begin{itemize} \itemsep -2pt 
	      \item Reorganized master photo collection using metadata, allowing for rapid photo search by keyword.
                 \item Created a visual representation of completed projects by exporting data from Excel into Google Fusion Tables. XML 			      was used to add additional information to data points from a spreadsheet. 
                 \item General IT and website consulting.
                 \end{itemize} 
                
 
\section{EXTRAS}             
           {\bf Teaching Assistant for Intro to Visual Basic (Fall 2012)}, 
            CS Crew,
            VT Hackathon.
	    See my work at \url{http://scperkins.github.io}
             

\end{resume}
\end{document}







